---
title: "Peer Graded ML"
author: "Chetan"
date: "10/21/2020"
output:
  word_document: default
  html_document: default
---

Week 4 PML project 
```{r}
library(caret)
library(knitr)

library(data.table)
library(rpart.plot)
library(rpart)

library(gbm)
library(ggplot2)

library(corrplot)

```
cleaning and then exploring the data. 

```{r}
Url <- "https://d396qusza40orc.cloudfront.net/predmachlearn/pml-testing.csv"
tra  <- "https://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv"

test <- read.csv(url(Url))
dtra <- read.csv(url(tra))


```
 cleaning the input of the data

```{r}
train_data <- dtra[, colSums(is.na(dtra)) == 0]
testing_data <- test[, colSums(is.na(test)) == 0]
```
 we will consider seventy percentage of the data for the training set and rest of the thirty percentage of the data for the testing data set

```{r}
train_data <- train_data[, -c(1:7)]
testing_data <- testing_data[, -c(1:7)]
dim(train_data)
```

```{r}
set.seed(1234)
dtraining <- createDataPartition(dtra$classe, p = 0.7, list = FALSE)
train_data <- train_data[dtraining, ]
testing_data <- train_data[-dtraining, ]
dim(train_data)
dim(testing_data)
```
removing the variables that are non zero .
```{r}
nZero <- nearZeroVar(train_data)
train_data <- train_data[, -nZero]
testing_data <- testing_data[, -nZero]
dim(train_data)
dim(testing_data)
```


```{r}
plot_cor <- cor(train_data[, -53])
corrplot(plot_cor, order = "FPC", method = "color", type = "upper", tl.cex = 0.8, tl.col = rgb(0, 0, 0))
```

Algorithms used:
trees and random forests 
n
```{r}
set.seed(20000)
tredec <- rpart(classe ~ ., data=train_data, method = "class")
rpart.plot(tredec)
```

 we will be validate the model 
```{r}
modelpre <- predict(tredec, testing_data, type = "class")
ab <- confusionMatrix(modelpre, testing_data$classe)
ab
```

```{r}
plot(modelpre)
```


```{r}
set.seed(10000)
ctr_gbm <- trainControl(method = "repeatedcv", number = 5, repeats = 1)
valid_gbm <- train(classe ~ .,data=train_data, method = "gbm", trControl = ctr_gbm, verbose = FALSE)
valid_gbm$finalModel
```


So finally i was able to do this project with the help of the videos i watched on coursera.
Basically we predicted how many did the exercise and the order in which they did it.
Thankyou



